%!TEX TS-program = xelatex
\documentclass[]{akers-cv}

\begin{document}
\header{andrew}{akers}
       {software engineer}


% In the aside, each new line forces a line break
\begin{aside}
  \section{about}
    1812 W 244th St
    Torrance, CA 90501
    ~
    \href{tel:13109013050}{310.901.3050}
    \href{mailto:andrew@akrs.me}{andrew@akrs.me}
    \href{http://akrs.me}{http://akrs.me}
    Tweet at me: \href{http://twitter.com/akrs_}{@akrs\_}
    Fork me: \href{http://github.com/akrs}{github/akrs}
  \section{programming}
    {\color{red} $\varheartsuit$} C, Java
    Javascript, Python, x86\_64 Assembly
    CSS3 \& HTML5
\end{aside}

\section{interests}

low level code, open source, security, tinkering

\section{education}

\begin{entrylist}
  \entry
    {since 2012}
    {BS in Computer Science}
    {Loyola Marymount University}
    {Expected graduation May 2016}
\end{entrylist}

\section{experience}

\begin{entrylist}
  \entry
    {2011-2015}
    {6th Street Consulting}
    {Intern}
    {Deployed and maintained small and medium business networks, both on premises and in AWS/Azure. Also worked with a team to build and deploy corporate intranets based on SharePoint for large clients.}
  \entry
    {since 2015}
    {SpaceX}
    {Mission and Launch Operations Intern}
    {Work with a small team to build and maintain a worldwide network of ground stations. Primary responsibilities were monitoring infrastructure and developing custom hardware and the software to run it.}
\end{entrylist}

\section{projects}

\begin{entrylist}
  \entry
    {2015}
    {Geoff}
    {\href{https://github.com/akrs/cmsi387}{GitHub}}
    {An operating system developed from first principals for CMSI 387. Built roughly along the lines of \href{http://littleosbook.github.io}{littleosbook.github.io}.}
  \entry
    {2014}
    {Wearables UI Research}
    {SCCUR}
    {Did a comparative analysis of the learnability of the UIs of Pebble, Android Wear, and Google Glass with a partner. Presented a poster at the Southern California Conference for Undergraduate Research.}
  \entry
    {2014}
    {PebbLIFX}
    {\href{https://github.com/jadengore/PebbLIFX}{GitHub}}
    {A Pebble application to control LIFX Bulbs from a Pebble. Built initially on AndroidLIFX, later moved to the official library.}
  \entry
    {2014}
    {AndroidLIFX}
    {\href{https://github.com/akrs/AndroidLIFX}{GitHub}}
    {Unofficial API to support LIFX bulbs in Android and Java applications}
  \entry
    {2014}
    {Captionr}
    {\href{http://https://github.com/alexschneider/Captionr}{GitHub}}
    {Website to automatically synchronize transcripts with a YouTube video. Built with a partner in 48 hours for LA Hacks.}
\end{entrylist}

\section{awards}
\begin{entrylist}
  \entry
    {2011}
    {Finalist}
    {CyberPatriot III}
    {Lead a team of 5 into the top 12 through an Air Force Association sponsored CyberSecurity competition, out of around 400 teams across the nation.}
  \entry
    {2010}
    {3rd Place}
    {CyberPatriot II}
    {Got third place in an Air Force Association sponsored CyberSecurity competition out of around 200 teams across the nation.}
 \end{entrylist}

\end{document}
